{\textbf \Large Final Exam} \hfill CSE 103, Fall 2014
\\

\vspace{.25in}

Name: \underline{\hspace{3in}}
\\

ID: \underline{\hspace{3.2in}}
\\

\vspace{0.5in}

On your desk you should have only the exam paper, writing tools, and
the cheat-sheet. The cheat-sheet is one page handwritten on both sides.

The exams are color coded. Your exam should have different color 
than that of your neighbours to the left, right and in front.

There are 11 questions in this exam, totalling 125 points.  The final
score is determined by summing all the points and taking the min of
the sum and 100. For a final grade of A+ it is necessary (but not
sufficient) to get more than 100 points in the final. 

Be clear and concise. Write your answers {\bf in the space provided}
after each question. Whenever possible, {\bf write your answers
as expressions, not as numbers}. If an expression is reused
later in the problem, you are encouraged to assign it to a letter
variable and use the variable in the later expressions. For example,
suppose in the first part of the problem you find the answer to be
$C(52,5)$ and that in a later part the answer is $22/C(52,5)$. You can
define in the first part $a=C(52,5)$ and write the second expression
as $22/a$. This will save you time and space and is easier for us to
grade.

Do your work at the empty space. If your answer is incorrect, we will
look at your work and give you credit if you were going in the right direction.

\vspace{0.2in}

\begin{center}
\begin{tabular}{|c|l|} \hline
\hspace{1in} & \hspace{1in} \\
1 & 12pt. \\ 
&  \\ \hline
2 & 9pt. \\
&  \\ \hline
3 & 10pt. \\
&  \\ \hline
4 & 10pt.\\
&  \\ \hline
5 & 10pt.\\
&  \\ \hline
6 & 9pt.\\
&  \\ \hline
7 & 9pt.\\
&  \\ \hline
8 & 9pt.\\
&  \\ \hline
9 & 20pt. \\
& \\ \hline
10 & 11pt. \\
& \\ \hline
11 & 16pt. \\
& \\ \hline
\end{tabular}
\end{center}
\begin{center}Total 125\end{center}

\vspace{0.2in}

This exam was graded by:\\
\hspace{1cm}abalsubr@eng.ucsd.edu
\hspace{1cm}iawwal@eng.ucsd.edu
\hspace{1cm}sjrao@eng.ucsd.edu
\hspace{1cm}zzhai@ucsd.edu
\hspace{1cm}yfreund@eng.ucsd.edu


\pagebreak
